Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
improved some wording in recent pass

  A $d$-representation is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
  The first $d$ rows of $V$ form a (not-necessarily-orthonormal, but normal) basis for $\reals^d$.
  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
  So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
  Taking the convex combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
  If $\alpha_1$ is positive, this implies there is slack in the $d$th constraint, so the halfspace representation cannot be tight.
  If $\alpha_1$ is positive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
  Choosing the $i+1$st column of $B$ as a constraint gives the contradiction as above.
\end{proof}
To recall what is happening inside this proof: we chose the first level set, which gave us a matrix $B$.
The first column was all-$1$, which corresponds to a constraint on the subgradient set of the loss on outcome $1$ for report $1$, which is not an interesting constraint.
The other constraints gave a contradiction if $d$ is too small.
\bo{More to say?}

>>>>

  A $d$-representation is therefore a $V$ with $n-1$ rows, each a unit vector $v_i$ in $\reals^d$.
  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
  The first $d+1$ rows are linearly dependent in $\reals^d$.
  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
  So if $w \in T$, then $\langle v_1,w \rangle \leq -1$ and $\langle v_i,w \rangle \leq 0$ for all $i=2,\dots,d$.
  Taking the weighted combination, we obtain $\langle v_{d+1}, w \rangle \leq -\alpha_1$.
  If $\alpha_1$ is positive, this implies there is slack in the $d$th constraint, so the halfspace representation cannot be tight.
  If $\alpha_1$ is positive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_{i'} > 0$.
  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
  Choosing the $i+1$st column of $B$ as a constraint gives the contradiction as above.
\end{proof}
To recall what is happening inside this proof: we chose the first level set, which gave us a matrix $B$.
The first column was all-$1$, which corresponds to a constraint on the subgradient set of the loss on outcome $1$ for report $1$, which is not an interesting constraint.
The other constraints gave a contradiction if $d$ is too small.
\bo{More to say?}
